The Atala PRISM Protocol

### 2022-12-19 prism-backend/research/prism-protocol/did_atala.tex
Beginning proof of Atala DIDs with global subroutines.

In this section we first describe Atala PRISM DID method \RealPKIDIDAtala, and
prove that it realizes \IdealGPKIDID.
%
We begin by describing the types of keys supported in Atala PRISM, and then
specify how sets of such keys can be managed through the previously introduced
dictionaries in \IdealGPKIDID.

@@

\paragraph{$\P_{Atala}$ policy.} %
Before proceeding with the specififying the DID operations in Atala, we define
its policy on the keys' labels and types.
\todo{This needs to take into account the caller, and the previous state of the
  PKI list.}

\begin{figure}[ht]
  \centering
  \procedure{$\P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})$}{    
    \pcif \exists i\in[n]~\suchthat~\typ_i \notin [\MasterKey,\IssueKey,
    \CommKey,\AuthKey]: \pcreturn 0~\pccomment{All types must be known} \\   
    \pcif \not\exists i\in[n]~\suchthat~\typ_i = \MasterKey: \pcreturn 0~
    \pccomment{There must be at least one master key} \\
    \pcif \exists i, j \in[n], i \neq j~\suchthat~\lbl_i = \lbl_j: \pcreturn 0~
    \pccomment{No duplicate labels} \\
    \pcreturn 1
  }
  \caption{Policy $\P_{Atala}$ that all DID documents must meet in Atala.}
\end{figure}

@@

\begin{description}
\item{\uccmd{Create}.} %
  To create a DID, the user has to specify the key pairs to create, along with
  fresh identifiers (labels) and their type. For ease of exposition, we assume
  that the used identifiers just follow a sequence. The predicate \P in Atala
  simply requires that at least one key pair of \MasterKey type is created. The
  \uccmd{Create} algorithm creates as many keys of each type as requested,
  and keeps a list with the identifier, type and public key of each key pair.
  This list is then hashed into a value \texttt{h}, and the created DID is
  ``\texttt{\did:prism:h}''. A transaction containing the created list, the
  DID, and the \texttt{CreateDID} instruction is sent to the blockchain,
  signed by one of the master keys -- w.l.o.g., we simply use the first one
  in the list. The DID owner stores locally the list, along with the
  corresponding private keys.
\item[\uccmd{Read}.] %
  Getting the contents of a DID simply requires processing the associated
  transactions in the blockchain. Namely, transactions $(\tx,\sig)$ where $\tx$
  is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
  \cdot)$. The associated DID Document is the result of applying in an ordered
  manner (from oldest to newest) all such validly signed transactions.
\item[\uccmd{Update}.] %
  To update a DID, we first assume for ease of exposition that the calling party
  $P$ has an updated version of the associated DID Document (which included
  a list of $n$ keys) -- if this is not the case, it suffices to make first a
  call to \uccmd{Read} for the given DID. \todo{This seems relevant enough to
    be highlighted in some more visible place, no?}
  Then, updating a DID requires to (optionally) specify a list of previously
  existing key identifiers to remove, and (optionally) specify a list of new key
  identifiers, and their types, to add. To simplify notation, we just adopt the
  (equivalent) convention that the caller indicates a list of $\lbrace (i,
  \lbl_i) \rbrace_{i\in\tilde{N}\subseteq[\tilde{n}]}$ pairs, where $\tilde{n}$
  may be smaller or larger than $n$, depending on the desired update. This
  list is then interpreted as follows. If $i$ is an already existing
  identifier, the label is ignored and the corresponding key is not removed. If
  $i$ is a new identifier, then a new key pair of the given type is created.
  Omitting an existing identifier is then interpreted as the desire to remove
  the corresponding key pair. Otherwise, the same policy as for \uccmd{Create}
  applies here. Key pairs for the new keys are generated, and a transaction is
  sent to the blockchain, signed with one of the master keys in the DID
  \emph{before applying the update}. This transaction contains a list of the
  identifiers of the keys to remove, and a list of the identifiers and types
  of the keys to add.
\item[\uccmd{Deactivate}.] %
  A deactivate operation is simply an update operation with no new key
  identifiers, and that only specifies the existing identifiers that will
  \emph{not} be deactivated.
\end{description}

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
          \pcif \P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}) = 0: abort \\
          \st \gets \emptyset \\
          \pcfor i \in [n]: \\
          \pcind \sid' \gets ((P,\lbl_i),\sid) \\
          \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st \gets \st \cup \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace \\
          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealGRO \\
          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealGRO \\
          \did \gets ``did:prism:''||~h \\
          \tx \gets (\texttt{CreateDID}, \did, \st) \\
          \lbl \gets \LMKL(\st); \sid' \gets ((P,\lbl),\sid) \\
          \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
          \text{Locally store}~
          (\did, \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]}) \\
          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i
          \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealGdledger \\
          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealGdledger \\
          \st \gets \emptyset \\
          L_{\did} \gets (\ast,\did,\ast) \subseteq \DID \\
          \pcfor (\tx=(\texttt{op},\did,\cdot),\sig) \in L_{\did}: \\
          \pcind \pk \gets \emptyset \\
          \pcind \pcif \texttt{op} = \texttt{CreateDID}~\land \\
          \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
          \pcind \pcind (\cdot,\cdot,\lbrace (\lbl_i,\typ_i,\pk_i)
          \rbrace_{i\in[n]}) \gets \tx \\
          \pcind \pcind \st \gets \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i \in [n]} \\
          \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
          \pcind \pcind (\cdot,\cdot,(\st_d,\st_a)) \gets \tx \\
          \pcind \pcind \lbrace \lbl^d_i \rbrace_{i\in[n^d]} \gets \st_d \\ 
          \pcind \pcind \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i)
          \rbrace_{i\in[n^a]} \gets \st_a \\
          \pcind \pcind \st \gets (\st \setminus \st_d) \cup \st_a \\
          \pcind \lbl \gets \LMKL(\st) \\
          \pcind \pcif \lbl = \emptyset \lor \P_{Atala}(\st) = 0: \text{skip} \\
          \pcind \pcelse \sid' \gets ((P,\lbl),\sid) \\
          \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{Verifd},\sid',\tx,b)~\text{from}~\IdealFSig \\
          \pcind \pcif b = 0: \text{skip} \\
          \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
        }    
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Create} and \texttt{Read} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
  \label{fig:atalapkidid1}
\end{figure}

@@

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.6\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \sval_d, \sval_a)$}{
          % \pcif \exists i~\suchthat~\typ_i \notin [\MasterKey,\AuthKey,
          % \CommKey,\IssueKey]~\lor \\
          % \pcind \nexists i~\suchthat~\typ_i = \MasterKey
          % \lor \exists i,j~\suchthat~\lbl_i = \lbl_j: abort \\
          % \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
          % \CommKey,\IssueKey] \lor
          % \nexists i~\suchthat~\lbl_i = \MasterKey: \\
          % \pcind abort \\
          % \text{Run $(\uccmd{Read},\sid,\did)$ to fetch $(\did,\sval)$} \\
          % \pcif \sval = \bot: abort \\
          \text{Fetch}~
          (\did, \sval=\lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]})
          ~\text{from storage} \\
          \st_a \gets \emptyset;~
          \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]} \gets \sval \\
          \lbrace \lbl^d_i \rbrace_{i\in[n_d]} \gets \sval_d;~
          \lbrace (\lbl^a_i,\typ^a_i) \rbrace_{i\in[n_a]} \gets \sval_a \\
          \sval' \gets (\sval \setminus \sval_d) \cup \sval_a
          \pccomment{\todo{Syntax refinement needed here.}} \\
          \pcif \P_{Atala}(\sval') = 0: abort \\          
          \pcfor i \in [n_a] \\
          \pcind \ucsend~(\uccmd{KeyGen},((P,\lbl_i),\sid))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},((P,\lbl_i),\sid),\pk^a_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_a \gets \st_a \cup \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i) \rbrace \\
          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
          \tx \gets (\texttt{UpdateDID}, \did, \sval_d, \st_a) \\
          \lbl \gets \LMKL(\sval) \\
          \ucsend~(\uccmd{Sign},((P,\lbl),\sid),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
          \text{Locally store}~(\did,\sval) \\
          \ucio{Output}~(\uccmd{Updated},\sid,(\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}))
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \sval)$}{       
          \text{Run as a \texttt{Update} operation} \\
          \text{with $\sval_d \gets \sval$ and $\sval_a \gets \emptyset$}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

@@

Before going into the proofs, observe that the \uccmd{Create} (in lines 1-2) and
\uccmd{Update} (in lines 6-7) operations in \RealPKIDIDAtala include a policy on
the received key labels and types. Concretely, this policy requires that all
labels are unique, all types are of a known key type, and that at least one of
them is of type \MasterKey. In the sequel, we use $\P_{Atala}$ to refer to this
policy.

\todo{Do we mention somewhere that {\sid}s have structure $(P,\sid')$? This is
  used for \Sim to know which party is generating which keys.}

\begin{theorem}[UC-security of \RealPKIDIDAtala]
  \label{thm:sec-didatala}
  \RealPKIDIDAtala UC-realizes $\IdealGPKIDID$ in the $(\IdealGRO,
  \IdealFSig, \IdealGdledger)$-hybrid model.
\end{theorem}

\begin{proof}
  We show that \RealPKIDIDAtala UC-realizes \IdealGPKIDID, when configured
  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
  \Exec_{\phiDID,\Sim,\Env}$,
  where \phiDID is a protocol composed with the same parties as
  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
  every message from \Env to the ideal functionality \IdealGPKIDID, and every
  response from \IdealGPKIDID back to \Env. The simulator \Sim runs internally a
  copy of the real-world adversary \adv, as well as the ideal functionalities
  \IdealGRO, \IdealFSig and \IdealGdledger, and any involved party.

  \begin{description}
  \item[Simulating DID Create.] %
    % 
    % Keys generation
    If \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,\typ_i)
    \rbrace_{i\in[n]})$ from \IdealGPKIDID, with $\sid=(P,\sid')$, it simulates
    the key generation process of $n$ signing key pairs run in the real
    protocol, by sending $n$ queries $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ to
    \adv~on behalf of \IdealFSig, and receiving the $n$ corresponding
    $(\uccmd{VerKey},((P,\lbl_i),\sid),\pk_i)$ responses.
    %
    % Hash computation
    \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
    simulates a query to \IdealGRO, to set \did as ``$did:prism: h$'' as DID
    value.
    %
    % Tx sim
    With the DID value, \Sim simulates for \adv~the preparation of transaction
    \tx. That is, \Sim uses the master key with lowest label, $\lbl \gets
    \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,\lbl),\sid),\tx)$ to
    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)$.
    %
    % BB append
    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealGdledger.
    %
    % Output
    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace \pk_i
    \rbrace_{i\in[n]})$ to \IdealGPKIDID, and stores the tuple $(P,\did,\lbrace
    (\lbl_i,\typ_i,\pk_i)\rbrace_{i\in[n]})$.
    %
    % Additional considerations
    \todo{The following should probably go to the argumentation part.}
    Note that \did is generated by an ideal random oracle (thus, uniformly at
    random), just as in the real protocol \RealPKIDIDAtala. Hence, the
    probability that \IdealGPKIDID halts because $\did \in \DID$ is negligible,
    and \IdealGPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i=\pk_i
    \rbrace_{i\in[n]})$ to \IdealGPKIDID.
  \item[Simulating DID Read.]
    To simulate read operations, when \Sim receives $(\uccmd{Read},\sid,\did)$
    from \IdealGPKIDID, it first simulates for \adv~the call to \IdealGdledger, to
    get the current status $L$ of the bulletin board. Then, \Sim reproduces the
    processing a normal party would do: from older to newer entry in $L$ related
    to \did, applies the updates in a sequential order -- ignoring any
    \uccmd{UpdateDID} operation before a \uccmd{CreateDID}, and only applying
    the first \uccmd{CreateDID}. If, after applying an update, $\P_{Atala}$ is
    not met by the resulting set of keys and labels, \Sim skips the update.
    Otherwise, \Sim simulates for \adv~a verification query to \IdealFSig for
    the transaction corresponding to the update, and skips the update if the
    signature fails.
    %
    Finally, if after processing all transactions related to \did, the resulting
    contents differ from those stored by \Sim in its record $(P,\did,\sval)$,
    \Sim aborts \todo{Do we need this?}. Otherwise, \Sim returns the processed
    contents.    
  \item[Simulating DID Update.]
    % Load DID
    Upon receiving a request from dummy party $P$, \IdealGPKIDID fetches
    $(P,\did,\sval)$ from its records, and checks if $(\sval \setminus \sval_d)
    \cup \sval_a$ meets $\P_{Atala}$. If either step fails, \IdealGPKIDID
    aborts. Else, it sends $(\uccmd{Update},\sid,\did,\sval_d,\sval_a)$ to \Sim.
    \Sim then retrieves $(P,\did,\sval)$ from its records \todo{this is kept at
      some point, no?)} and simulates for \adv~the calls to \IdealFSig for the
    keys in the received $\sval_a$. \Sim gets the key with the lowest label from
    \sval, with label $\lbl$, bundles the transaction \tx, and simulates a call
    to \IdealFSig to get a signature over \tx. Finally, \Sim simulates the call
    to \IdealGdledger, and returns $(\uccmd{Updated},\sid,(\did,\lbrace \val_i
    \rbrace_{i\in[n_a]}))$ to \IdealGPKIDID, where the $\val_i$'s are the values
    output by \adv~when creating the new keys via simulated calls to \IdealFSig.

>>>>

In this section we first describe Atala PRISM DID method \RealPKIDIDAtala, and
prove that it realizes \IdealGPKIDID.
%
We begin by describing the types of keys supported in Atala PRISM, and the
policy \PAtala that all CRUD operations need to meet.

@@

\paragraph{\PAtala policy.} %
Before proceeding with the specififying the DID operations in Atala, we define
its policy on the keys' labels and types.
\todo{This needs to take into account the caller, and the previous state of the
  PKI list.}

\begin{figure}[ht]
  \centering
  \procedure{$\PAtala(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})$}{    
    \pcif \exists i\in[n]~\suchthat~\typ_i \notin [\MasterKey,\IssueKey,
    \CommKey,\AuthKey]: \pcreturn 0~\pccomment{All types must be known} \\   
    \pcif \not\exists i\in[n]~\suchthat~\typ_i = \MasterKey: \pcreturn 0~
    \pccomment{There must be at least one master key} \\
    \pcif \exists i, j \in[n], i \neq j~\suchthat~\lbl_i = \lbl_j: \pcreturn 0~
    \pccomment{No duplicate labels} \\
    \pcreturn 1
  }
  \caption{Policy \PAtala that all DID documents must meet in Atala.}
\end{figure}

@@

\begin{description}
\item{\uccmd{Create}.} %
  To create a DID, the user has to specify the fresh identifiers (labels) and
  types of the key pairs to include in the DID. The \uccmd{Create} algorithm
  creates as many keys of each type as requested, by leveraging the ideal
  functionality \IdealFSig, and keeps a list with the identifier, type and
  public key of each key pair. This list is then hashed into a value \texttt{h}
  via \IdealGRO, and the created DID is ``\texttt{\did:prism:h}''. A transaction
  containing the created list, the DID, and the \texttt{CreateDID} instruction
  is sent to the blockchain via a call to \IdealGdledger, signed by one of the
  master keys -- w.l.o.g., we 
  simply use the first one in the list. The DID owner stores locally the list.
\item[\uccmd{Read}.] %
  Getting the contents of a DID simply requires processing the associated
  transactions in the blockchain. Namely, the interface first fetches all the
  contents from the \IdealGdledger functionality. Then, transactions the
  relevant transactions are those with $(\tx,\sig)$ where $\tx$
  is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
  \cdot)$. The associated DID Document is the result of applying in an ordered
  manner (from oldest to newest) all such validly signed transactions.
\item[\uccmd{Update}.] %
  To update a DID, we first assume for ease of exposition that the calling party
  $P$ has an updated version of the associated DID Document (which included
  a list of $n$ keys) -- if this is not the case, it suffices to make first a
  call to \uccmd{Read} for the given DID.
  %
  Then, updating a DID requires to (optionally) specify a list of previously
  existing key labels to remove $\sval_d$, and (optionally) specify a list
  $\sval_a$ of new key labels and their types to add. The result of removing
  the labels in $\sval_d$ and adding the new keys in $\sval_a$ must satisfy
  \PAtala. Key pairs for the new keys are generated via \IdealFSig, and a
  transaction is sent to the blockchain via \IdealGdledger, signed (again, via
  \IdealFSig) with one of the master keys in the DID \emph{before applying the
    update}. This transaction contains a list of the identifiers of the keys to
  remove, and a list of the identifiers and types of the keys to add.
  %
  Note that the DID remains the same, even though the original contents of
  the associated DID document may change.
\item[\uccmd{Deactivate}.] %
  A deactivate operation is simply an update operation with no new key
  identifiers, and that only specifies the existing identifiers that will
  \emph{not} be deactivated.
\end{description}

@@

    \scalebox{0.9}{
      \begin{minipage}[t]{0.55\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
          \pcif \PAtala(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}) = 0: abort \\
          \st \gets \emptyset \\
          \pcfor i \in [n]: \\
          \pcind \sid' \gets ((P,\lbl_i),\sid) \\
          \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
          \IdealFSig \\
          \pcind \st \gets \st \cup \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace \\
          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealGRO \\
          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealGRO \\
          \did \gets ``did:prism:''||~h \\
          \tx \gets (\texttt{CreateDID}, \did, \st) \\
          \lbl \gets \LMKL(\st); \sid' \gets ((P,\lbl),\sid) \\
          \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Submit},(\tx,\sig))~\text{to}~\IdealGdledger \\
          \text{Locally store}~
          (\did, \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]}) \\
          \ucio{Output}~(\uccmd{ProcessedC},\sid,\did,\lbrace \pk_i
          \rbrace_{i\in[n]})
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Read} \land
          \arg = did$}{
          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealGdledger \\
          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealGdledger \\
          \st \gets \emptyset \\
          L_{\did} \gets (\ast,\did,\ast) \subseteq \DID \\
          \pcfor (\tx=(\texttt{op},\did,\cdot),\sig) \in L_{\did}: \\
          \pcind \pk \gets \emptyset \\
          \pcind \pcif \texttt{op} = \texttt{CreateDID}~\land \\
          \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
          \pcind \pcind (\cdot,\cdot,\lbrace (\lbl_i,\typ_i,\pk_i)
          \rbrace_{i\in[n]}) \gets \tx \\
          \pcind \pcind \st \gets \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i \in [n]} \\
          \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
          \pcind \pcind (\cdot,\cdot,(\st_d,\st_a)) \gets \tx \\
          \pcind \pcind \lbrace \lbl^d_i \rbrace_{i\in[n^d]} \gets \st_d \\ 
          \pcind \pcind \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i)
          \rbrace_{i\in[n^a]} \gets \st_a \\
          \pcind \pcind \st \gets (\st \setminus \st_d) \cup \st_a \\
          \pcind \lbl \gets \LMKL(\st) \\
          \pcind \pcif \lbl = \emptyset \lor \PAtala(\st) = 0: \text{skip} \\
          \pcind \pcelse \sid' \gets ((P,\lbl),\sid) \\
          \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{Verifd},\sid',\tx,b)~\text{from}~\IdealFSig \\
          \pcind \pcif b = 0: \text{skip} \\
          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\st)
        }    
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Create} and \texttt{Read} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
  \label{fig:atalapkidid1}
\end{figure}

@@

    \scalebox{0.90}{          
      \begin{minipage}[t]{0.6\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (did, \sval_d, \sval_a)$}{
          \text{Fetch}~
          (\did, \sval=\lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]})
          ~\text{from storage} \\
          \st_a \gets \emptyset;~
          \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]} \gets \sval \\
          \lbrace \lbl^d_i \rbrace_{i\in[n_d]} \gets \sval_d;~
          \lbrace (\lbl^a_i,\typ^a_i) \rbrace_{i\in[n_a]} \gets \sval_a \\
          \sval' \gets (\sval \setminus \sval_d) \cup \sval_a
          \pccomment{\todo{Syntax refinement needed here.}} \\
          \pcif \PAtala(\sval') = 0: abort \\          
          \pcfor i \in [n_a] \\
          \pcind \ucsend~(\uccmd{KeyGen},((P,\lbl_i),\sid))~\text{to}~\IdealFSig \\
          \pcind \ucrecv~(\uccmd{VerKey},((P,\lbl_i),\sid),\pk^a_i)~\text{from}~
          \IdealFSig \\
          \pcind \st_a \gets \st_a \cup \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i) \rbrace \\
          \tx \gets (\texttt{UpdateDID}, \did, \sval_d, \st_a) \\
          \lbl \gets \LMKL(\sval) \\
          \ucsend~(\uccmd{Sign},((P,\lbl),\sid),\tx)~\text{to}~\IdealFSig \\
          \ucrecv~(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
          \ucsend~(\uccmd{Submit},(\tx,\sig))~\text{to}~\IdealGdledger \\
          \text{Locally store}~(\did,\sval) \\
          \ucio{Output}~(\uccmd{ProcessedU},\sid,\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}) \\
          \text{\todo{The previous must return all the final pks, not only
              $pk^a$, to be compatible with deact.}}
        }
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.45\textwidth}
        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (did, \sval)$}{       
          \text{Run as an \texttt{Update} operation with} \\
          \text{ $\sval_d \gets \sval$ and $\sval_a \gets \emptyset$,
            and output} \\
          \text{\uccmd{ProcessedD} instead of \uccmd{ProcessedU}}
        }
      \end{minipage}
    }
  \end{framed}
  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
  \label{fig:atalapkidid2}
\end{figure}

@@

We prove security of \RealPKIDIDAtala by showing that it UC-emulates
\IdealGPKIDID. For this, we leverage concretely the results in \cite{bch+20} and
\cite{bhz21}. In a nutshell, the former extends the notions of UC emulation and
composition so that they are compatible, in the plain UC model, with global
subroutines (such as a global clock, a ledger, or a random oracle).
\cite{bhz21} builds on these results to make them suitable for systems that rely
simultaneously on multiple global functionalities.
%
To make the previous a bit more precise, we replicate here the relevant theorem
from \cite{bhz21} (in \cite{bch+20}, the same statement appears with only one
global subroutine).

\begin{theorem}[UC emulation with multiple global setups \cite{bhz21}]
  \label{thm:uc-bhz21}
  Let $\pi$, $\phi$ and $\gamma_1,\dots,\gamma_n$ be protocols. We say that
  $\pi$ $\xi$-UC-emulates $\phi$ in the presence of global subroutines
  $\gamma_1,\dots,\gamma_n$ if protocols $\pi$ and $\phi$ are formulated with
  respect to a global subroutine $\hat{\gamma}_{\gamma_1,\dots,\gamma_n}$ and
  $\UCM[\pi,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$ $\xi$-emulates protocol
  $\UCM[\phi,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$.
\end{theorem}

At a high level, to apply the results in \cite{bch+20,bzh21}, we show the global
subroutines used in \IdealGPKIDID and \RealPKIDIDAtala can be merged into the
single ``meta'' global subroutine $\hat{\gamma}_{\gamma_1,\dots,\gamma_n}$
required by \thmref{thm:uc-bhz21}, which furthermore meets the conditions to be
subsequently suitable for UC-emulation. In addition, we argue that this is
usually the case for the known realisations of each respective global
subroutine. (This ensures that our approach is natural, and indeed UC-realisable
in practice.)
%
We then describe how the management protocol \UCM works in conjunction with
our \IdealGPKIDID and the ``meta'' global subroutines (in the ideal world), and
with \RealPKIDIDAtala and the ``meta'' global subroutine (in the real world).
%
Finally, we show that the latter emulates the former.
%
We emphasise that this is merely an application of the results in
\cite{bch+20,bhz21} to our setting. The previously sketched process is detailed
next, directly referencing the relevant theorems of the relevant works, when
appropriate.

\paragraph{The meta-global subroutine \gAtala.} %
We next show that the global subroutines used in \RealPKIDIDAtala are leveraged
in a way that is compatible with \cite[Theorem 4.3]{bhz21}. This is not a full
proof for a concrete application of such theorem, as that would require proving
that concrete protocols UC-emulate each global functionality. However, we
initially leave it ``incomplete'' to show that any combination of instantiations
of our global subroutines can be used to build a secure variant of the Atala
DID protocol (later, we show the concrete instantiations that Atala currently
uses). For concreteness, we refer to this ``partial'' property as mergability
of the global subroutines of Atala into \gAtala.

\begin{lemma}[Mergability of \gAtala]
  \label{lma:gAtala}
  Let $\gamma_1 \gets \IdealGdledger$, $\gamma_2 \gets \IdealGRO$, $\gamma_3
  \gets \IdealGclock$. Then:
  \begin{enumerate}
  \item For $i < 3$, $\gamma_i$ is subroutine respecting except for calls to
    $\gamma_{i+1,\dots,3}$, and $\gamma_3$ is subroutine respecing. All
  $\gamma_i$'s are subroutine exposing.
\item For $i>1$, $\gamma_i$ is $\gamma_j$-regular, for all $j \in \set{1,
    \dots,\i-1}$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  \qed
\end{proof}

% Before going into the proofs, observe that the \uccmd{Create} (in lines 1-2) and
% \uccmd{Update} (in lines 6-7) operations in \RealPKIDIDAtala include a policy on
% the received key labels and types. Concretely, this policy requires that all
% labels are unique, all types are of a known key type, and that at least one of
% them is of type \MasterKey. In the sequel, we use \PAtala to refer to this
% policy.

% \todo{Do we mention somewhere that {\sid}s have structure $(P,\sid')$? This is
%   used for \Sim to know which party is generating which keys.}

% \begin{theorem}[UC-security of \RealPKIDIDAtala]
%   \label{thm:sec-didatala}
%   \RealPKIDIDAtala UC-realizes $\IdealGPKIDID$ in the $(\IdealGRO,
%   \IdealFSig, \IdealGdledger)$-hybrid model.
% \end{theorem}

% \begin{proof}
%   We show that \RealPKIDIDAtala UC-realizes \IdealGPKIDID, when configured
%   with policy \PAtala. For this, we give a simulator \Sim such that, for
%   any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
%   \Exec_{\phiDID,\Sim,\Env}$,
%   where \phiDID is a protocol composed with the same parties as
%   \RealPKIDIDAtala but where each party is simply a dummy party that forwards
%   every message from \Env to the ideal functionality \IdealGPKIDID, and every
%   response from \IdealGPKIDID back to \Env. The simulator \Sim runs internally a
%   copy of the real-world adversary \adv, as well as the ideal functionalities
%   \IdealGRO, \IdealFSig and \IdealGdledger, and any involved party.

%   \begin{description}
%   \item[Simulating DID Create.] %
%     % 
%     % Keys generation
%     If \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,\typ_i)
%     \rbrace_{i\in[n]})$ from \IdealGPKIDID, with $\sid=(P,\sid')$, it simulates
%     the key generation process of $n$ signing key pairs run in the real
%     protocol, by sending $n$ queries $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ to
%     \adv~on behalf of \IdealFSig, and receiving the $n$ corresponding
%     $(\uccmd{VerKey},((P,\lbl_i),\sid),\pk_i)$ responses.
%     %
%     % Hash computation
%     \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
